Jane, John … Leslie? A Historical Method for Algorithmic Gender Detection

### 2014-09-19 article.Rmd
Wickham Tidy Data article is out now

These two datasets (and any future datasets to be added to the package) thus contain a simple table of data. ^[The format of this data departs from the more generally desirable "tidy data" framework proposed by Hadley Wickham for performance reasons. By keeping the data in a "wider" format instead of a tidy format as defined by Wickham, the function is able to make its predictions faster [Wickham forthcoming].] The columns contain the `name`, `year`, and number of `female` and `male` uses of that name in a particular year.

@@

Bird et al. 2009. Bird, Steve, Edward Loper, and Ewan Klein, *Natural Language Processing with Python* (O’Reilly, 2009)

@@

Wickham, forthcoming. Hadley Wickham, "Tidy Data." *Journal of Statistical Software* (forthcoming), http://vita.had.co.nz/papers/tidy-data.html.

Wickham and Francois 2014-. Wickham, Hadley and Romain Francois, *dplyr: dplyr: a grammar of data manipulation*. R package version 0.2 (2014): <http://CRAN.R-project.org/package=dplyr>.

>>>>

These two datasets (and any future datasets to be added to the package) thus contain a simple table of data. ^[The format of this data departs from the more generally desirable "tidy data" framework proposed by Hadley Wickham for performance reasons. By keeping the data in a "wider" format instead of a tidy format as defined by Wickham, the function is able to make its predictions faster [Wickham 2014b].] The columns contain the `name`, `year`, and number of `female` and `male` uses of that name in a particular year.

@@

Bird et al. 2009. Bird, Steve, Edward Loper, and Ewan Klein, *Natural Language Processing with Python* (O’Reilly, 2009).

@@

Wickham 2014. Hadley Wickham, "Tidy Data." *Journal of Statistical Software*, 50 (2014): http://www.jstatsoft.org/v59/i10.

Wickham and Francois 2014. Wickham, Hadley and Romain Francois, *dplyr: dplyr: a grammar of data manipulation*. R package version 0.2 (2014): <http://CRAN.R-project.org/package=dplyr>.
